Hamby Data and `rtrees`

### 2019-09-13 README.Rmd
small updates to journal and readme

>>>>

- Sometimes LIME does not want to run in R

```{r error = TRUE, message = FALSE}
library(caret)
library(lime)

# Split up the data set
iris_test <- iris[1:5, 1:4]
iris_train <- iris[-(1:5), 1:4]
iris_lab <- iris[[5]][-(1:5)]

# Create Random Forest model on iris data
model <- train(iris_train, iris_lab, method = 'rf')

# Create an explainer object
explainer <- lime(iris_train, model)

# Explain new observation
explanation <- explain(iris_test, explainer, n_labels = 1, n_features = 2)
```

### 2019-09-13 journals/01-hamby_data_and_models/01-hamby_data_and_models.Rmd
small updates to journal and readme

---
title: "Hamby Data and `rtrees`"
author: "Katherine Goode"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
---

@@

```{r}
# Load libraries
library(bulletr)
library(cowplot)
library(glmnet)
library(plotly)
library(randomForest)
library(tidyverse)
```

@@

>>>>

---
title: "Hamby Data and `rtrees`"
author: "Katherine Goode"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    theme: cerulean
    highlight: textmate
---

@@

```{r}
# Load libraries
library(bulletr)
library(cowplot)
library(GGally)
library(glmnet)
library(plotly)
library(randomForest)
library(tidyverse)
```

@@

##### Feature Interactions

```{r}
hamby224_test %>%
  select(rf_features, samesource) %>%
  ggpairs(mapping = aes(color = samesource), 
          columns = rf_features)
```
